Constant Error Tolerance Computational Fuzzy Extractors

### 2014-02-06 constantRate/ConstCompFuzzExt.tex
Revised security of second cons arg

Both of constructions are based on the obfuscation of point programs.  A point program $I_w(x)$ outputs $1$ if $x=w$ and $0$ otherwise.  Intuitively, an obfuscated version of a program reveals nothing past its input and output behavior.  For a point program, this means hiding all partial information about the point $w$.  Obfuscation for this class of functions is achievable under particular number-theoretic assumptions~\cite{canetti1997towards} and from generic cryptographic hardness assumptions~\cite{wee2005obfuscating}.  Both constructions are inspired by Canetti and Dakdouk's construction of digital lockers from point obfuscation~\cite{canetti2008obfuscating}.

@@

\begin{definition}~\cite[Definition 2.5]{fuller2013computational}
\label{def:comp fuzzy extractor}
Let $\mathcal{W}$ be a family of probability distributions over $\mathcal{M}$. A pair of randomized procedures ``generate'' $(\gen)$ and ``reproduce'' $(\rep)$ is a $(\mathcal{M}, \mathcal{W}, \kappa, t)$-\emph{computational fuzzy extractor} that is $(\epsilon, s_{sec})$-hard with error $\delta$ if \gen and \rep satisfy the following properties:
\begin{itemize}
\item The generate procedure \gen on input $w\in \mathcal{M}$ outputs an extracted string $R\in\{0,1\}^\kappa$ and a helper string $P\in\{0,1\}^*$.
\item The reproduction procedure \rep takes an element $w'\in\mathcal{M}$ and a bit string $P\in\{0,1\}^*$ as inputs.  The \emph{correctness} property guarantees that if $\dis(w, w')\leq t$ and $(R, P)\leftarrow \gen(w)$, then $\Pr[\rep( w', P) = R] \geq 1-\delta$ where the probability is over the randomness of $(\gen, \rep)$.
If $\dis(w, w') > t$, then no guarantee is provided about the output of \rep.
\item The \emph{security} property guarantees that for any distribution $W\in \mathcal{W}$, the string $R$ is pseudorandom conditioned on $P$, that is $\delta^{\mathcal{D}_{s_{sec}}}((R, P), (U_\kappa, P))\leq \epsilon$.
\end{itemize}
\end{definition}
In the above definition, the errors are chosen before $P$: if the error pattern between $w$ and $w'$ depends on the output of $\gen$ there is no guarantee about the probability of correctness. In both our constructions it is crucial that $w'$ is chosen independently of the outcome of \gen.
The definition of computational fuzzy extractors specifies a family of sources for which the fuzzy extractor works rather than the family of all sources of a given min-entropy $m$.  With $\Huse<0$ this is necessary for any meaningful security~(see \apref{sec:minimal conditions}).

@@

\section{A Constant Error-Tolerance Computational Fuzzy Extractor}
\label{sec:construction}
For the remainder of this work, we consider the Hamming metric over some alphabet $\mathcal{Z}$.  Our goal is to derive strong keys for a large class of sources where $0>\Huse = \Hoo(W) - \log|B_t|$.
In the computational setting a ``long enough'' key may be expanded using a computational extractor~(\lemref{lem:cond and cext}).  We focus on building a computational fuzzy conductor with meaningful output entropy.  Our first construction is inspired by the construction of digital lockers from point obfuscation by Canetti and Dakdouk~\cite{canetti2008obfuscating}.

@@

\begin{definition}
\label{def:block guessable}
Let $\mathcal{O}_{w_1,..., w_\ell}$ be an oracle that returns \[\mathcal{O}_{w_1,..., w_\ell}(i, w_i')=
\begin{cases}
1 & w_i = w_i'\\
0 & \text{otherwise}.
\end{cases}
\]
A source $W = W_1||...|W_\ell$ is a $(q, \alpha, \beta)$-\emph{unguessable block distribution} \lnote{is it ''block unguessable'' or ''unguessable block''? the usage is inconsistent}if there exists a set $\mathcal{I}\subset\{1,..., \ell\}$ of size at least $\ell -\beta$ such that for any unbounded adversary $A$ with oracle access to $\mathcal{O}$ making at most $q$ queries
\[
\forall i\in \mathcal{I}, \Hav(W_i |View(A^{\mathcal{O}_{W}(\cdot, \cdot)}))\geq \alpha.
\]
\end{definition}

%\noindent We argue security assuming that the adversary knows the value of all blocks outside of $\mathcal{I}$.
We discuss  block unguessable distributions in \apref{sec:characterize}.  \consref{cons:first construction} is secure for block unguessable distributions:
\begin{theorem}
\label{thm:security of cons}
Let $\mathcal{O}$ be an $\ell$-composable VGB obfuscator with auxiliary inputs for point programs over $\mathcal{Z}$. 
Let $W$ be a $(s_{obf}, \alpha = \omega(\log n), \beta)$-unguessable block distribution.  For every $s_{sec} = \poly(n)$ there exists some $\epsilon_{sec} = \ngl(n)$ such that $H^{\hill}_{\epsilon_{sec}, s_{obf}}( C | P ) \geq |C| - \beta$.% for $\epsilon' = 2\epsilon_{obf} + (\ell-\beta)2^{-(\alpha - 1)}$.
\end{theorem}

@@

Together, with the arguments in \secref{sec:sec of construction} we have the construction is secure and correct for block unguessable distributions:
\begin{theorem}
Let $\mathcal{W}$ be the family of $(q,\alpha= \omega(\log n),  \beta)$-unguessable distributions over $\zo^{n\times \ell}$ for any $q = \poly(n)$.  Furthermore, let $C$ be a $(\neigh_t, \delta_{code})$-code.  Then for $s_{sec} = \poly(n)$ there exists some $\epsilon=\ngl(n)$ such that \consref{cons:first construction} is a $(\zo^{n\times \ell}, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta_{code} + \ell/2^n$ and resulting entropy $\tilde{m} =\log |C| - \beta$.
\end{theorem}
\begin{proof}
Security is a result of \thref{thm:security of cons}.  Correctness follows from \lemref{lem:correct of cons}.
\end{proof}

@@

To show that $\Huse$ can be negative for \consref{cons:first construction}, we first calculate the size of the Hamming ball.  We allow $t$ errors with an alphabet $\mathcal{Z}$ of size $2^n$.  This means that
\begin{align*}
\log |B_t| &= \log \sum_{i=0}^t {\ell \choose i} (|\mathcal{Z}|-1)^i\\
&> \log {\ell \choose t} (2^n-1)^t\\
&=\Theta(tn) + \log {\ell\choose t}
% \log (2^n)^{H_{2^n}(t/\ell)\ell - o(\ell)} =n( H_{2^n}(t/\ell)\ell -o(\ell) )
\end{align*}

We consider what entropy is necessary for security.  The simplest type of block unguessable distribution is where each block is independent and has super-logarithmic entropy~(\clref{cl:independent high ent}).  For this type of source the required entropy is $\Hoo(W) = \ell\omega(\log n)$.  This yields:
\[
\Huse = \Hoo(W) - \log |B_t| < \ell \omega(\log n) -\left( \Theta(t n) + \log {\ell \choose t}\right).
\]
When $t =\Theta(\ell)$, then $\Huse<0$ and the output entropy is $|C| -\beta$~(if $C$ is a constant rate, this is $\Theta(\ell)$).
Thus, \consref{cons:first construction} achieves negative $\Huse$ when $t = \Theta(\ell)$.  We achieve $\Huse<0$, constant error tolerance, and extract a constant fraction of $n$ when $t = \Theta(\ell)$ and $\ell = O(n)$.
%When $ \ell , t, n$ to be the same order provides a natural balance of parameters.

@@

\defref{def:unordered source} is a generalization of block sources~(introduced by Chor and Goldreich~\cite{DBLP:journals/siamcomp/ChorG88}) where blocks must have entropy conditioned on the value of previous blocks.  An unordered block source is also a strengthening of an unguessable block distribution~(\defref{def:block guessable}).  An unordered block source requires there to be worst case entropy while an unguessable block distribution only requires average conditional entropy.  However, we achieve security for significantly lower entropy levels than were needed for block unguessable distributions.

We use an algorithm that selects a fixed size random subset of $\{1,..., \gamma\}$.  Let $\sample_{\gamma, \eta}(\cdot)$ be an algorithm that outputs a random subset of $\{1,..., \gamma\}$ of size $\eta$ and let $r_{sam}$ the number of required coins for $\sample_{\gamma, \eta}$.
\begin{construction}
\label{cons:sampling}
Let $n$ be a security parameter.
Let $\mathcal{Z}$ be an alphabet, and let $W = W_1,..., W_\gamma$ be a source where each $W_i$ is over $\mathcal{Z}$ and $\gamma = \Omega(n)$.  Let $\ell = O(\poly(n)) = \omega(\log n)$ and let $C\subset \zo^\ell$ be a $(\neigh_{t'}, \delta_{code})$.   Let $\eta = \omega(\log n)$ and let $\mathcal{O}$ be a $\ell$-composable VGB obfuscator with auxiliary input for the family of point functions over $ \mathcal{Z}^\eta$.  Define $\gen, \rep$ as:

@@

\subsection{Security of \consref{cons:sampling}}
\bnote{this whole chain of arguments needs to be cleaned up}
\bnote{went through the surrounding text, need to look at all the theorem statements}
In order to show security \consref{cons:sampling}, we show that with overwhelming probability each of the selected $V_i$ has super-logarithmic entropy on its own~(samplers will select ``enough'' of the good blocks of $W$ each time).  We can then argue that $V_1,..., V_\ell$ forms a block-unguessable distribution.  Then \consref{cons:sampling} is just the first construction applied to $V_1,.., V_\ell$ and security follows by \thref{thm:security of cons}.  We begin by showing that each $V_i$ is statistically close to a high entropy distribution.

\begin{lemma}
\label{lem:sampling works}
Let $W = W_1,..., W_\gamma$ be a $(\alpha = \Omega(1), \beta \leq \gamma(1/2-\Theta(1)))$-unordered block source.  Let $\eta = \Omega(\log n)$. Consider some fixed $i$, the distribution $V_{i}, \Lambda_i$ is $(\ngl(n)+ 2^{-\Omega(n)})$-close to a distribution $V', U_{r_{sam}}$ where for all $u\in U_{r_{sam}}$ $V' | U_{r_{sam}}=u$, $\Hoo(V' | U_{r_{sam}}=u) \geq \Omega(\alpha\times (1-2\times \beta) \times \eta) = \omega(\log n) = \alpha'$.
\end{lemma}
\begin{proof}
By~\cite[Lemma 9]{vadhan2003constructing}, noting that the na\"{i}ve sampler is optimum in necessary samples and we use $\eta = \omega(\log n)$ samples.  \bnote{need someone to check parameters, in the abstract, I am fairly sure the statement makes sense, but I could easily have messed something up}\bnote{even if this is right it needs to be expanded.  too much for a reader to digest.}
\end{proof}

\noindent
We can then argue that all $V_i$ simultaneously have individual entropy with good probability:
\begin{corollary}
\label{cor:samp sec}
Let $W = W_1,..., W_\gamma$ be a $(\alpha = \Omega(1), \beta \leq \gamma /2-\Omega(1))$-unordered block source.  Let $\eta = \Omega(\log n)$.  Denote by $\epsilon_{sam} = \ngl(n) + 2^{-\Omega(n)} = \ngl(n)$ the value from \lemref{lem:sampling works}.
Then, the distribution $(V, \Lambda)$ is $(\ell\epsilon_{sam})$-close to a distribution $(V', U_{\ell\times r_{sam}})$ where for $u\in U_{\ell\times r_{sam}}$ for all $i$, $\Hoo(V_i' | U_{\ell\times r_{sam}} =u)\geq \alpha'$.
\end{corollary}
\begin{proof}
Hybrid argument over the statistical distance in \lemref{lem:sampling works}.
\end{proof}

In the \apref{sec:characterize} we show that any distribution where each individually block has super-logarithmic min-entropy forms a block unguessable distribution~\clref{cl:all blocks entropy}.  This allows us to conclude:
\begin{corollary}
\label{cor:v are unguessable}
Let $W, V, \Lambda, V', U_{\ell\times r_{sam}}$ be as in \corref{cor:samp sec}.
Let $q = \poly(n)$, there exists some $\alpha'' = \omega(\log n)$ such that distribution $V' , U_{\ell\times r_{sam}}$ is a $(q, \alpha'', 0)$-block unguessable distribution.
\end{corollary}

Finally, since $V_1,..., V_\ell$ is statistically close~(conditioned on the randomness of $\sample$) to a block unguessable distribution, \consref{cons:sampling} is just \consref{cons:first construction} applied to $V_1,..., V_\ell$.
\begin{corollary}
\label{cor:samp unguess}
Let $n, \mathcal{Z}, W, \epsilon_{sam}$ be as in \corref{cor:samp sec} and let $\mathcal{O}$ is an $\ell$-composable VGB obfuscator with auxiliary inputs for point programs over $\zo^{\beta\times \log |\mathcal{Z}|}$, then for every $s_{sec} = \poly(n)$ there exists $\epsilon_{sec} = \ngl(n)$ such that $H^{\hill}_{\epsilon_{sec}, s_{sec}}(C | P) \geq |C|$. %for $\epsilon' = (2\epsilon_{obf} + \ell(\epsilon_{sam}+ 2^{-(\alpha''-1)})) = \ngl(n)$.
\end{corollary}
\begin{proof}
Result of \corref{cor:v are unguessable} and \thref{thm:security of cons}.
\end{proof}

@@

\defref{def:block guessable} is an inherently adaptive definition and thus a little unwieldy for a distribution.  In this section, we partially characterize sources that satisfy \defref{def:block guessable}.
The majority of the difficulty in characterizing \defref{def:block guessable} is that different blocks may be dependent, so an equality query on block $i$ may shape the distribution of block $j$.  Thus, we begin with the case of independent blocks.

\begin{claim}
\label{cl:independent high ent}
Let $W = W_1,  ... , W_\ell$ be a source in which all blocks $W_i$  are mutually independent.  Let $\alpha$ be a parameter.  Let $\mathcal{I}\subset \{1,..., \ell\}$ be a set of indices such that for all $i\in\mathcal{I}$, $\Hoo(W_i ) =\alpha $.  Then for any $q$, $W$ is a $(q, \alpha - \log (q+1), \ell - |\mathcal{I}|)$-block unguessable distribution.  In particular, when $\alpha = \omega(\log n)$ and $q = \poly(n)$, then $W$ is a $(q, \omega(\log n), \ell - |\mathcal{I}|)$-block unguessable distribution.
\end{claim}
\begin{proof}
It suffices to show that for all $i\in \mathcal{I}, \Hav(W_i |View(A^{\mathcal{O}_{W}(\cdot, \cdot)}) = \alpha -\log q$.
We can ignore queries for all blocks but the $i$th, as the blocks are independent. Furthermore, without loss of generality, we can assume that no duplicate queries are asked, and that the adversary is deterministic (we can hardwire the best coins as nonuniform advice). Let $A_1, A_2, \dots A_q$ be the random variables representing the oracle answers for an  adversary $\mathcal{A}$ \lnote{is the adversary $S$, $\mathcal{A}$, or $A$?} making $q$  queries about the $i$th block. Each $A_j$ is just a bit, and at most one of them  is equal to 1 (because duplicate queries are disallowed). Thus, the total number of possible responses is $q+1$. Thus, we have the following,
\begin{align*}
\Hav(W_i | View(A^{\mathcal{O}_{W}(\cdot, \cdot)}) &= \Hav(W_i| A_1, \dots, A_q)\\
&=\Hoo(W_i) - H_0(A_1, \dots, A_q)\\
&=\alpha - \log (q+1)\,,
\end{align*}
where the second line follows from the first by~\cite[Lemma 2.2]{DBLP:journals/siamcomp/DodisORS08}.
\end{proof}
\noindent In their work on computational fuzzy extractors, Fuller, Meng, and Reyzin~\cite{fuller2013computational} show a construction for block-fixing sources, where each block is either uniform or a fixed symbol~(block fixing sources were introduced by Kamp and Zuckerman~\cite{KZ07}).  \clref{cl:independent high ent} captures, in particular, this class of distributions.

However, \defref{def:block guessable} captures considerably more distributions.  We now consider more complicated distributions where blocks are not independent.

>>>>

Both of constructions are based on the obfuscation of point programs.  A point program $I_w(x)$ outputs $1$ if $x=w$ and $0$ otherwise.  Intuitively, an obfuscated version of a program reveals nothing past its input and output behavior.  For a point program, this means hiding all partial information about the point $w$.  Obfuscation for this class of functions is achievable under particular number-theoretic assumptions~\cite{canetti1997towards} and from generic cryptographic hardness assumptions~\cite{wee2005obfuscating}.  We need a strong version of point obfuscation secure under composition, this is achievable under a particular number-theoretic assumption~\cite{bitansky2010strong}.  Both constructions are inspired by Canetti and Dakdouk's construction of digital lockers from point obfuscation~\cite{canetti2008obfuscating}.

@@

\begin{definition}~\cite[Definition 2.5]{fuller2013computational}
\label{def:comp fuzzy extractor}
Let $\mathcal{W}$ be a family of probability distributions over $\mathcal{M}$. A pair of randomized procedures ``generate'' $(\gen)$ and ``reproduce'' $(\rep)$ is a $(\mathcal{M}, \mathcal{W}, \kappa, t)$-\emph{computational fuzzy extractor} that is $(\epsilon, s_{sec})$-hard with error $\delta$ if \gen and \rep satisfy the following properties:
\begin{itemize}
\item The generate procedure \gen on input $w\in \mathcal{M}$ outputs an extracted string $R\in\{0,1\}^\kappa$ and a helper string $P\in\{0,1\}^*$.
\item The reproduction procedure \rep takes an element $w'\in\mathcal{M}$ and a bit string $P\in\{0,1\}^*$ as inputs.  The \emph{correctness} property guarantees that if $\dis(w, w')\leq t$ and $(R, P)\leftarrow \gen(w)$, then $\Pr[\rep( w', P) = R] \geq 1-\delta$ where the probability is over the randomness of $(\gen, \rep)$.
If $\dis(w, w') > t$, then no guarantee is provided about the output of \rep.
\item The \emph{security} property guarantees that for any distribution $W\in \mathcal{W}$, the string $R$ is pseudorandom conditioned on $P$, that is $\delta^{\mathcal{D}_{s_{sec}}}((R, P), (U_\kappa, P))\leq \epsilon$.
\end{itemize}
\end{definition}
In the above definition, the errors are chosen before $P$: if the error pattern between $w$ and $w'$ depends on the output of $\gen$ there is no guarantee about the probability of correctness. In both our constructions it is crucial that $w'$ is chosen independently of the outcome of \gen.
The definition of computational fuzzy extractors specifies a family of sources for which the fuzzy extractor works rather than the family of all sources of a given min-entropy $m$.  With $\Huse<0$ some restriction is necessary for any meaningful security~(see \apref{sec:minimal conditions}).  Instead of restricting the class of source distributions~(for which security is achieved), the definition could restrict the error model to errors that are ``likely'' to occur in the source.  We leave this as an open problem.

@@

\section{A Computational Fuzzy Extractor when $\Huse<0$}
\label{sec:construction}
For the remainder of this work, we consider the Hamming metric over some alphabet $\mathcal{Z}$.  Our goal is to derive strong keys for a large class of sources where $0>\Huse = \Hoo(W) - \log|B_t|$.
In the computational setting a ``long enough'' key may be expanded using a computational extractor~(\lemref{lem:cond and cext}).  We focus on building a computational fuzzy conductor with meaningful output entropy.  Our first construction is inspired by the construction of digital lockers from point obfuscation by Canetti and Dakdouk~\cite{canetti2008obfuscating}.

@@

\begin{definition}
\label{def:block guessable}
Let $\mathcal{O}_{w_1,..., w_\ell}$ be an oracle that returns \[\mathcal{O}_{w_1,..., w_\ell}(i, w_i')=
\begin{cases}
1 & w_i = w_i'\\
0 & \text{otherwise}.
\end{cases}
\]
A source $W = W_1||...|W_\ell$ is a $(q, \alpha, \beta)$-\emph{unguessable block distribution} if there exists a set $\mathcal{I}\subset\{1,..., \ell\}$ of size at least $\ell -\beta$ such that for any unbounded adversary $A$ with oracle access to $\mathcal{O}$ making at most $q$ queries
\[
\forall i\in \mathcal{I}, \Hav(W_i |View(A^{\mathcal{O}_{W}(\cdot, \cdot)}))\geq \alpha.
\]
\end{definition}

%\noindent We argue security assuming that the adversary knows the value of all blocks outside of $\mathcal{I}$.
We discuss unguessable block distributions in \apref{sec:characterize}.  \consref{cons:first construction} is secure for unguessable block distributions:
\begin{theorem}
\label{thm:security of cons}
Let $\mathcal{O}$ be an $\ell$-composable VGB obfuscator with auxiliary inputs for point programs over $\mathcal{Z}$. 
Let $W$ be a $(s_{obf}, \alpha = \omega(\log n), \beta)$-unguessable block distribution.  For every $s_{sec} = \poly(n)$ there exists some $\epsilon_{sec} = \ngl(n)$ such that $H^{\hill}_{\epsilon_{sec}, s_{obf}}( C | P ) \geq |C| - \beta$.% for $\epsilon' = 2\epsilon_{obf} + (\ell-\beta)2^{-(\alpha - 1)}$.
\end{theorem}

@@

Together, with the arguments in \secref{sec:sec of construction} we have the construction is secure and correct for unguessable block distributions:
\begin{theorem}
Let $\mathcal{W}$ be the family of $(q,\alpha= \omega(\log n),  \beta)$-unguessable distributions over $\mathcal{Z}^\ell$ for any $q = \poly(n)$.  Furthermore, let $C$ be a $(\neigh_t, \delta_{code})$-code.  Then for $s_{sec} = \poly(n)$ there exists some $\epsilon=\ngl(n)$ such that \consref{cons:first construction} is a $(\mathcal{Z}^\ell, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta_{code} + \ell/2^n$ and resulting entropy $\tilde{m} =\log |C| - \beta$.
\end{theorem}
\begin{proof}
Security is a result of \thref{thm:security of cons}.  Correctness follows from \lemref{lem:correct of cons}.
\end{proof}

@@

To show that $\Huse$ can be negative for \consref{cons:first construction}, we first calculate the size of the Hamming ball.  We allow $t$ errors with an alphabet $\mathcal{Z}$ of size $2^n$.  This means that
\begin{align*}
\log |B_t| &= \log \sum_{i=0}^t {\ell \choose i} (|\mathcal{Z}|-1)^i\\
&> \log {\ell \choose t} (2^n-1)^t\\
& =\Theta(tn) + \log {\ell\choose t}
% \log (2^n)^{H_{2^n}(t/\ell)\ell - o(\ell)} =n( H_{2^n}(t/\ell)\ell -o(\ell) )
\end{align*}

We consider what entropy is necessary for security.  The simplest type of unguessable block distribution is where each block is independent and has super-logarithmic entropy~(\clref{cl:independent high ent}).  For this type of source the required entropy is $\Hoo(W) = \ell\omega(\log n)$.  This yields:
\[
\Huse = \Hoo(W) - \log |B_t| < \ell \omega(\log n) -\left( \Theta(t n) + \log {\ell \choose t}\right).
\]
When $t =\Theta(\ell)$, then $\Huse<0$ and the output entropy is $|C| -\beta$~(if $C$ is a constant rate, this is $\Theta(\ell)$).
Thus, \consref{cons:first construction} achieves for security for unguessable block distributions with negative $\Huse$ when $t = \Theta(\ell)$.  %We achieve security when $\Huse<0$, constant error tolerance, and extract a constant fraction of $n$ when $t = \Theta(\ell)$ and $\ell = O(n)$.
%When $ \ell , t, n$ to be the same order provides a natural balance of parameters.

@@

\defref{def:unordered source} is a generalization of block sources~(introduced by Chor and Goldreich~\cite{DBLP:journals/siamcomp/ChorG88}) where blocks must have entropy conditioned on the value of previous blocks.  An unordered block source is also a strengthening of an unguessable block distribution~(\defref{def:block guessable}).  An unordered block source requires there to be worst case entropy while an unguessable block distribution only requires average conditional entropy.  However, we achieve security for significantly lower entropy levels than were needed for unguessable block distributions.

We use an algorithm that selects a fixed size random subset of $\{1,..., \gamma\}$.  Let $\sample_{\gamma, \eta}(\cdot)$ be an algorithm that outputs a random subset of $\{1,..., \gamma\}$ of size $\eta$ and let $r_{sam}$ the number of required coins for $\sample_{\gamma, \eta}$.
\begin{construction}
\label{cons:sampling}
Let $n$ be a security parameter.
Let $\mathcal{Z}$ be an alphabet, and let $W = W_1,..., W_\gamma$ be a source where each $W_i$ is over $\mathcal{Z}$ and $\gamma = \Omega(n)$.  Let $\ell = O(\poly(n)) = \omega(\log n)$ and let $C\subset \zo^\ell$ be a $(\neigh_{t'}, \delta_{code})$.   Let $\eta = \omega(\log n) = o(\gamma)$ and let $\mathcal{O}$ be a $\ell$-composable VGB obfuscator with auxiliary input for the family of point functions over $ \mathcal{Z}^\eta$.  Define $\gen, \rep$ as:

@@

\subsection{Security of \consref{cons:sampling}}
In order to show security \consref{cons:sampling}, we show that with overwhelming probability each of the selected $V_i$ has super-logarithmic entropy on its own~(samplers will select ``enough'' of the good blocks of $W$ each time).  We can then argue that $V_1,..., V_\ell$ forms a block-unguessable distribution.  Then \consref{cons:sampling} is just the first construction applied to $V_1,.., V_\ell$ and security follows by \thref{thm:security of cons}.  We begin by showing that each $V_i$ is statistically close to a high entropy distribution.

%\bnote{think about how to make this work when $\eta = \Theta(1)$.  Will make probabilities gross.  Probably not for submission.}
\begin{lemma}
\label{lem:sampling works}
Let $W = W_1,..., W_\gamma$ be a $(\alpha = \Omega(1), \beta\le \gamma(1- \Theta(1)))$-unordered block source and let $\eta = \omega(\log n) \le  o(\gamma)$.  Consider some fixed $i$, there exists $\epsilon_{sam} = O(e^{-\eta}) = \ngl(n)$ and $\alpha' = \alpha\eta(\gamma-\beta-\eta)/\gamma = \omega(\log n)$ such that 
\[
\Pr[\Hoo(V_i | \Lambda) \geq \alpha'] \geq 1- \epsilon_{sam}.
\]
\end{lemma}
\begin{proof}
Consider some fixed $i$.  Let $\Lambda$ represent the random variable of all the coins used by $\sample$ and $\lambda$ be some particular outcome.
For each particular value of $w_1,..., w_\gamma$ there exists some set $\mathcal{I}$ of size $\gamma - \beta = \Theta(\gamma)$ such that each block $j\in \mathcal{I}, \Hoo(W_j | W_1 = w_1,..., W_{j-1}=w_{j-1}, W_{j+1}=w_{j+1},..., W_\gamma = w_\gamma) \geq \alpha$.  Since this is a worst case guarantee for all $\lambda$, 
\[
\Hoo(V_i |\lambda ) \geq \alpha \times |\{\text{indices in }\mathcal{I}\text{ sampled in }V_i\}|.
\]

Denote by $X = |\{\text{indices in }\mathcal{I}\text{ sampled in }V_i\}|$.  We now calculate $\expe[X]$.  Let $j_1,.., j_\eta$ be the elements selected by sampling algorithm.  The ``first'' element $j_1$ lands in $\mathcal{I}$ with probability $(\gamma-\beta)/\gamma$.  For each selected index $j_k$ there are least remaining $\gamma-\beta-k$ samples in $\mathcal{I}$, so $\Pr[j_k\in\mathcal{I}]>(\gamma-\beta-\eta)/\gamma$.  We can associate with each $j_k$ a Bernoulli random variable $X_k$ with success probability at least $(\gamma-\beta-\eta)/\gamma$ and note that 
\[
\expe[X] = \sum_{k=1}^\eta\expe[X_k] \geq \eta \expe[X_\eta]\geq \eta\frac{\gamma-\beta-\eta}{\gamma}.
\]
Using the Chernoff bound, $X$ rarely is far from its expected value:
\[
\Pr\left[ \frac{1}{\eta} \sum_{k=1}^\eta X_i \leq 1/2 \expe[X_i]\right]\leq 2e^{-\expe[X_i] \eta} = O(e^{-\eta})
\]
Where the last equality follows because 
\[
\expe[ X_i] = \frac{\gamma-\beta-\eta}{\gamma} \geq \frac{\Theta(\gamma) - \eta}{\gamma} = \frac{\Theta(\gamma) - o(\gamma)}{\gamma} = O(1).
\]
That is \[
\Pr[\Hoo(V_i ) \geq \alpha \times \frac{\eta(\gamma-\beta-\eta)}{2\gamma} = \alpha'] \geq 1- O(e^{-\eta}).
\]
\end{proof}

%
%\begin{lemma}
%
%Let $W = W_1,..., W_\gamma$ be a $(\alpha = \Omega(1), \beta \leq \gamma(1/2-\Theta(1)))$-unordered block source.  Let $\eta = \Omega(\log n)$. Consider some fixed $i$, the distribution $V_{i}, \Lambda_i$ is $(\ngl(n)+ 2^{-\Omega(n)})$-close to a distribution $V', U_{r_{sam}}$ where for all $u\in U_{r_{sam}}$ $V' | U_{r_{sam}}=u$, $\Hoo(V' | U_{r_{sam}}=u) \geq \Omega(\alpha\times (1-2\times \beta) \times \eta) = \omega(\log n) = \alpha'$.
%\end{lemma}
%\begin{proof}
%By~\cite[Lemma 9]{vadhan2003constructing}, noting that the na\"{i}ve sampler is optimum in necessary samples and we use $\eta = \omega(\log n)$ samples.  \bnote{need someone to check parameters, in the abstract, I am fairly sure the statement makes sense, but I could easily have messed something up}\bnote{even if this is right it needs to be expanded.  too much for a reader to digest.}
%\end{proof}

\noindent
We can then argue that all $V_i$ simultaneously have individual entropy with good probability:
\begin{corollary}
\label{cor:samp sec}
Let $W = W_1,..., W_\gamma$ be a $(\alpha = \Omega(1), \beta \leq \gamma(1-\Theta(1)))$-unordered block source.  Let $\eta = \omega(\log n) = o(\gamma)$ and let $\epsilon_{sam}, \alpha'$ be as in \lemref{lem:sampling works}.  Then $\Pr[\exists i, \Hoo(V_i | \Lambda) \not \ge \alpha'] \leq 1-\ell\epsilon_{sam}$.
%[V_i(V, \Lambda)$ is $(\ell\epsilon_{sam})$-close to a distribution $(V', U_{\ell\times r_{sam}})$ where for $u\in U_{\ell\times r_{sam}}$ for all $i$, $\Hoo(V_i' | U_{\ell\times r_{sam}} =u)\geq \alpha'$.
\end{corollary}
\begin{proof}
Union bound over the probability in \lemref{lem:sampling works}.
%Hybrid argument over the statistical distance in \lemref{lem:sampling works}.
\end{proof}

In the \apref{sec:characterize} we show that any distribution where each individually block has super-logarithmic min-entropy forms a unguessable block distribution~\clref{cl:all blocks entropy}.  This allows us to conclude:
\begin{corollary}
\label{cor:v are unguessable}
Let $W, V, \Lambda$ be as in \corref{cor:samp sec}.
Let $q = \poly(n)$, for $\alpha'' =\alpha'-1-\log (q+1) =  \omega(\log n)$ the distribution $V , \Lambda$ is $\ell \epsilon_{sam}$ statistically close to a $(q, \alpha'', 0)$-unguessable block distribution.
\end{corollary}

Finally, since $V_1,..., V_\ell$ is statistically close~(conditioned on the randomness of $\sample$) to a unguessable block distribution, \consref{cons:sampling} is \consref{cons:first construction} applied to $V_1,..., V_\ell$.
\begin{corollary}
\label{cor:samp unguess}
Let $n, \mathcal{Z}, W, \epsilon_{sam}$ be as in \corref{cor:samp sec} and let $\mathcal{O}$ is an $\ell$-composable VGB obfuscator with auxiliary inputs for point programs over $\zo^{\beta\times \log |\mathcal{Z}|}$, then for every $s_{sec} = \poly(n)$ there exists $\epsilon_{sec} = \ngl(n)$ such that $H^{\hill}_{\epsilon_{sec}, s_{sec}}(C | P) \geq |C|$. %for $\epsilon' = (2\epsilon_{obf} + \ell(\epsilon_{sam}+ 2^{-(\alpha''-1)})) = \ngl(n)$.
\end{corollary}
\begin{proof}
Result of \corref{cor:v are unguessable} and \thref{thm:security of cons} noting that $\ell \epsilon_{sam} = \ngl(n)$.
\end{proof}

@@

\defref{def:block guessable} is an inherently adaptive definition and thus a little unwieldy for a distribution.  In this section, we partially characterize sources that satisfy \defref{def:block guessable}.
The majority of the difficulty in characterizing \defref{def:block guessable} is that different blocks may be dependent, so an equality query on block $i$ may shape the distribution of block $j$.  Thus, we begin with the case of independent blocks.  In all of the examples that follow we denote the adversary by $S$ as we need security against the computationally unbounded adversary defined in VGB obfuscation~(\defref{def:obf}).

\begin{claim}
\label{cl:independent high ent}
Let $W = W_1,  ... , W_\ell$ be a source in which all blocks $W_i$  are mutually independent.  Let $\alpha$ be a parameter.  Let $\mathcal{I}\subset \{1,..., \ell\}$ be a set of indices such that for all $i\in\mathcal{I}$, $\Hoo(W_i ) =\alpha $.  Then for any $q$, $W$ is a $(q, \alpha - \log (q+1), \ell - |\mathcal{I}|)$-unguessable block distribution.  In particular, when $\alpha = \omega(\log n)$ and $q = \poly(n)$, then $W$ is a $(q, \omega(\log n), \ell - |\mathcal{I}|)$-unguessable block distribution.
\end{claim}
\begin{proof}
It suffices to show that for all $i\in \mathcal{I}, \Hav(W_i |View(A^{\mathcal{O}_{W}(\cdot, \cdot)}) = \alpha -\log (q+1)$.
We can ignore queries for all blocks but the $i$th, as the blocks are independent. Furthermore, without loss of generality, we can assume that no duplicate queries are asked, and that the adversary is deterministic (we can hardwire the best coins as nonuniform advice). Let $A_1, A_2, \dots A_q$ be the random variables representing the oracle answers for an  adversary $S$ making $q$  queries about the $i$th block. Each $A_j$ is just a bit, and at most one of them  is equal to 1 (because duplicate queries are disallowed). Thus, the total number of possible responses is $q+1$. Thus, we have the following,
\begin{align*}
\Hav(W_i | View(A^{\mathcal{O}_{W}(\cdot, \cdot)}) &= \Hav(W_i| A_1, \dots, A_q)\\
&=\Hoo(W_i) - |A_1, \dots, A_q|\\
&=\alpha - \log (q+1)\,,
\end{align*}
where the second line follows from the first by~\cite[Lemma 2.2]{DBLP:journals/siamcomp/DodisORS08}.
\end{proof}
\noindent In their work on computational fuzzy extractors, Fuller, Meng, and Reyzin~\cite{fuller2013computational} show a construction for block-fixing sources, where each block is either uniform or a fixed symbol~(block fixing sources were introduced by Kamp and Zuckerman~\cite{KZ07}).  \clref{cl:independent high ent} shows that \defref{def:block guessable} captures, in particular, this class of distributions.
However, \defref{def:block guessable} captures more distributions.  We now consider more complicated distributions where blocks are not independent.
